Size matters: Divergent morphology in elliptical bifaces from sites in the American Southeast articulates with distinct local reduction practices

### 2022-09-01 supp/index.Rmd
<edit index>

American Southeast, Caddo, archaeology, anthroinformatics, archaeoinformatics, museum studies, digital humanities, geometric morphometrics, STEM, STEAM, Jowell knife, Jowell knives, lithics, parallel-oblique flaking

@@

```{r figillust, fig.cap="Illustrated elliptical bifaces from the ancestral Caddo area highlighting parallel-oblique flaking used in production."}

>>>>

American Southeast, Caddo, archaeology, anthroinformatics, archaeoinformatics, museum studies, digital humanities, geometric morphometrics, STEM, STEAM, Jowell knife, Jowell knives, lithics, oblique parallel flaking

@@

```{r figillust, fig.cap="Illustrated elliptical bifaces from the ancestral Caddo area highlighting oblique parallel flaking used in production."}
